\begin{song}{title=The Bard's Song, band=Blind Guardian}
    \begin{multicols}{2}
        \begin{intro}
            You know it. \\
        \end{intro}

        \begin{bridge}
            ^{Am}Now You all ^{G}know, \\
            The ^{Em7}bards and their ^{Am}songs. \\
        \end{bridge}

        \begin{verse}
            When ^{Am}hours have gone ^{G}by, \\
            ^{Em7}I'll close my ^{Am}eyes. \\
            In a ^{Am}world far ^{G}away, \\
            We ^{Em7}may meet ^{Am}again. \\
            But ^{Am}now hear my ^{G}song, \\
            About the ^{Em7}dawn of the ^{Dm}night. \\
            Let's ^{C}sing ^{G}the ^{Am}bards' ^{G}song \ldots \\
        \end{verse}

        \begin{chorus}
            ^{Dm}Tomor - ^{Am}row will ^{Dm}take us ^{Am}away, \\
            ^{Dm}Far from ^{Am}home, \\
            ^{Dm}No one will ^{F}ever ^{G}know our ^{Dm}names, \\
            But the ^{Am}bards' songs ^{G}will ^{Am}remain. \\
            ^{Dm}Tomor - ^{Am}row will ^{Dm}take it ^{Am}away, \\
            The ^{Dm}fear of ^{Am}today, \\
            ^{F}It will be gone, \\
            Due ^{C}to our ^{G}magic ^{Em}songs. \\
        \end{chorus}

        \begin{verse}
            There's ^{Am}only one ^{G}song, \\
            ^{Em7}Left in my ^{Am}mind. \\
            ^{Am}Tales of a ^{G}brave man, \\
            Who ^{Em7}lived far from ^{Am}here. \\
            Now the ^{Am}bard songs are ^{G}over, \\
            And ^{Em7}it's time to ^{Am}leave. \\
            No ^{Am}one should ^{G}ask You \\
            for the ^{Em7}name of the ^{Am}one, \\
            ^{C}Who ^{G}tells ^{Am}the ^{G}story. \\
        \end{verse}

        \begin{chorus}
            ^{Dm}Tomor - ^{Am}row will ^{Dm}take us ^{Am}away, \\
            ^{Dm}Far from ^{Am}home, \\
            ^{Dm}No one will ^{F}ever ^{G}know our ^{Dm}names, \\
            But the ^{Am}bards' songs ^{G}will ^{Am}remain. \\
            ^{Dm}Tomor - ^{Am}row ^{Dm}all will be ^{Am}known, \\
            And ^{Dm}You're not ^{Am}alone, \\
            So ^{Dm}don't be ^{F}afraid, \\
            In the ^{G}dark and ^{Dm}cold, \\
            'Cause the ^{Am}bards' songs ^{G}will ^{Am}remain, \\
            They ^{C}all ^{G}will ^{Am}remain. \\
        \end{chorus}

        \begin{outro}
            ^{C}In my ^{G}thoughts and ^{Am}in my dreams, \\
            They're ^{C}always ^{G}in my ^{Am}mind, \\
            These ^{C}songs of ^{G}hobbits, ^{Am}dwarves and men, \\
            And ^{C}elves, Come ^{G}close your ^{Am}eyes. \\
            You can ^{C}see ^{G}them, ^{Em7}too \\
        \end{outro}
    \end{multicols}
\end{song}