Hello there! This is my first tab. The reason i did this one is because when i
tried looking up this song before, people only had the lyrics from the MOVIE "The
Hobbit" I wanted to do one with ALL the lyrics from the book. I hope you enjoy!
And please give me feedback. I want to know it anything is wrong or misplaced :) Thanks!


[Verse 1]

  Em      D      Bm       Em
Far over the misty mountain cold
          D        Bm      Em
To dungeons deep and caverns old
     G        D         Bm
We must away ere break of day
         Em      D       Em
To seek the pale enchanted gold.


[Verse 2]

             Em        D   Bm    Em
The dwarves of yore made mi--ghty spells,
            D         Bm      Em
While Hammers fell like ringing bells
         G           D          Bm
In places deep, where dark things sleep,
        Em        D       Em
In hallow halls beneath the fells.


[Verse 3]

           Em     D   Bm  Em
For ancient king and el-vish lord
             D       Bm     Em
There many a gleaming golden hoard
                G           D           Bm
They shaped the wrought, and light they caught
          Em     D       Em
To hide in gems on hilt of sword


[Verse 4]

            Em   D  Bm   Em
On silver necklaces th-ey strung
             D         Bm         Em
The flowering stars, on crowns they hung
          G         D       Bm
The dragon-fire, in twisted wire
               Em       D       Em
They meshed the light of moon and sun.


[Verse 5]

   Em       D        Bm     Em
Far over the misty mountains cold
           D        Bm      Em
To dungeons deep and caverns old
       G         D       Bm
We must away, ere break of day,
           Em     D        Em
To claim our long-Forgotten gold.


[Verse 6]

             Em    D    Bm    Em
Goblets they carved there for themselves
            D             Bm   Em
And harps of gold; where no man delves
           G         D      Bm
There lay a long, and many a song
        Em        D        Em
Was sung unheard by men or elves.


[Verse 7]

                 Em  D   Bm   Em
They pines were roaring on the height,
               D    Bm      Em
The winds were moaning in the night.
           G        D        Bm
The fire was red, in flaming spread;
              Em      D           Em
The trees like torches blazed with light.


[Verse 8]

  Em           D    Bm      Em
The bells were ringing in the dale
             D       Bm     Em
And men looked up with faces pale;
           G           D         Bm
The dragon's ire more fierce then fire
               Em        D      Em
Laid low there towers and houses frail.


[Verse 9]

              Em     D     Bm  Em
The mountains smoked beneath the moon;
                D         Bm      Em
The dwarves, the heard the tramp of doom.
               G      D     Bm
They fled there hall to dying fall
           Em     D          Em
Beneath his feet, beneath the moon.


[Verse 10]

   Em        D      Bm      Em
Far over the misty mountains grim
           D        Bm     Em
To dungeons deep and caverns dim
       G         D       Bm
We must away, Ere break of day,
          Em        D        Em
To win our harps and gold from him!


Über die Nebelberge weit,
Zu Höhlen tief aus alter Zeit,
Da ziehn wir hin, da lockt Gewinn
An Gold und Silber und Geschmeid.
Wo einst das Reich der Zwerge lag,
Wo glockengleich ihr Hammerschlag
Manch Wunder weckt, das still versteckt
Schlief in Gewölben unter Tag.

Das Gold und Silber dieser Erd
Geschürft, geschmiedet und vermehrt.
Sie fingen ein im edlen Stein
Das Licht als Zierart für das Schwert.

An Silberkettchen Stern an Stern,
Der Sonn- und Mondlichts reiner Kern,
Von Drachenblut die letzte Glut
Ging ein in Kronen großer Herrn.

Über die Nebelberge weit,
Zu Höhlen tief aus alter Zeit,
Dahin ich zieh in aller Früh
Durch Wind und Wetter, Not und Leid.

Aus goldnen Bechern, ganz für sich,
Da zechten sie allabendlich
Bei Harfenklang und Chorgesang,
Wo manche Stunde schnell verstrich.

Und knisternd im Gehölz erwacht
Ein Brand. Von Winden angefacht,
Zum Himmel rot die Flamme loht.
Bergwald befackelte die Nacht.

Die Glocken läuteten im Tal,
Die Menschen wurden stumm und fahl.
Der große Wurm im Feuersturm
Sengt’ ihre Länder schwarz und kahl.

Die Zwerge traf das Schicksal auch,
Im Mondschein stand der Berg in Rauch.
Durchs Tor entflohn, sanken sie schon
Dahin in seinem Feuerhauch.

Über die Nebelberge hin
Ins wilde Land lockt der Gewinn.
Dort liegt bereits seit alter Zeit,
Was unser war von Anbeginn.
